### 2018-04-13 tex/paper.tex
Add escrow example to paper

The whole contract remains as follows:
\begin{haskellcode}
CommitCash (IdentCC 1) 1
           (ConstMoney 100)
           10 200
           (CommitCash (IdentCC 2) 2
                       (ConstMoney 20)
                       20 200
                       (When (PersonChoseSomething (IdentChoice 1) 1)
                             100
                             (Both (RedeemCC (IdentCC 1) Null)
                                   (RedeemCC (IdentCC 2) Null))
                             (Pay (IdentPay 1) 2 1
                                  (ConstMoney 20)
                                  200
                                  (Both (RedeemCC (IdentCC 1) Null)
                                        (RedeemCC (IdentCC 2) Null))))
                       (RedeemCC (IdentCC 1) Null))
           Null
\end{haskellcode}
In the next section, we cover the online contract visualisation and interaction tool for Marlowe.

>>>>

The whole contract remains as follows:
\begin{haskellcode}
CommitCash (IdentCC 1) 1
           (ConstMoney 100)
           10 200
           (CommitCash (IdentCC 2) 2
                       (ConstMoney 20)
                       20 200
                       (When (PersonChoseSomething (IdentChoice 1) 1)
                             100
                             (Both (RedeemCC (IdentCC 1) Null)
                                   (RedeemCC (IdentCC 2) Null))
                             (Pay (IdentPay 1) 2 1
                                  (ConstMoney 20)
                                  200
                                  (Both (RedeemCC (IdentCC 1) Null)
                                        (RedeemCC (IdentCC 2) Null))))
                       (RedeemCC (IdentCC 1) Null))
           Null
\end{haskellcode}

In the next section, we look at how to take advantage of Haskell embedding when implementing Marlowe contracts.

\section{Haskell embedding example}
\label{section:example}

In this section, we give an example of how we can have Marlowe contracts that are easier to write, read, and 
understand, by embedding them into Haskel code (taking advantage that Marlowe contracts are implemented as Haskell 
terms).

The example contract we use through this section implements an escrow contract. Let us imagine that ``participant 1'' 
is buying some item from ``participant 2''. On one hand, if ``participant 1'' pays before receiving the item, there 
is a risk that ``participant 2'' will never give ``participant 1'' the item. On the other hand, if ``participant 2'' 
gives ``participant 1'' the item before ``participant 1'' pays, then there is a risk that ``participant 1'' will never 
pay.

The escrow mechanism allows ``participant 1'' to deposit the money into a contract, in a way that the money will only 
be released when two out of three participants agree on whether ``participant 2'' has indeed given ``participant 1'' 
the item. The third participant (``participant 3'') is supposed to be a neutral third party that will decide in case of 
dispute.

This way, if ``participant 1'' and ``participant 2'' are honest, they will just agree on the result of the transaction 
and ``participant 3'' will not need to do anything. If ``participant 1'' and ``participant 2'' disagree, ``participant 
3'' will be able to choose whether the money must go to ``participant 1'' or to ``participant 2''.

In addition to this, in our implementation, the money paid for the item is 450 ADA, it must be committed by 
``participant 1'' before block 10, and it will be refunded to ``participant 1'' if there is no consensus before block 
90.

We start by defining some Haskell functions. We can encapsulate identifiers in functions to make the contract more 
readable. That way we can generate an identifier for the cash commitment:

\begin{haskellcode}
iCC1 :: IdentCC
iCC1 = IdentCC 1
\end{haskellcode}

And an identifier for the payment:

\begin{haskellcode}
iP1 :: IdentPay
iP1 = IdentPay 1
\end{haskellcode}

We can also create a sub-contract that allows the money to be redeemed by ``participant 1'':

\begin{haskellcode}
redeem_original :: Contract
redeem_original = RedeemCC iCC1 Null
\end{haskellcode}

Each participant has a say on who deserves the money: either ``participant 1'' deserves a refund, which we represent 
with the number $0$; or ``participant 2'' deserves a payment, which we represent with the number $1$. Because there is 
only one choice to make per participant, we use the same \haskellinline{IdentChoice} as their participant id. We can 
define a function that returns an observation that is true if and only if the participant \haskellinline{per} has 
chosen the number \haskellinline{c} as follows:

\begin{haskellcode}
chose :: Int -> ConcreteChoice -> Observation
chose per c = PersonChoseThis (IdentChoice per) per c
\end{haskellcode}

Then we can easily write a function that returns an observation that is true if and only if at least one of the 
participants \haskellinline{per} and \haskellinline{per'} has chosen the number \haskellinline{c} as follows:

\begin{haskellcode}
one_chose :: Person -> Person -> ConcreteChoice -> Observation
one_chose per per' val = (OrObs (chose per val) (chose per' val)) 
\end{haskellcode}

After that, we can write a function that returns an observation that is true if and only if at least 
two of the three participants \haskellinline{p1}, \haskellinline{p2}, and \haskellinline{p3} have chosen the number 
\haskellinline{c} as follows:

\begin{haskellcode}
two_chose :: Person -> Person -> Person -> ConcreteChoice -> Observation
two_chose p1 p2 p3 c = OrObs (AndObs (chose p1 c) (one_chose p2 p3 c))
                             (AndObs (chose p2 c) (chose p3 c))
\end{haskellcode}

Finally, we can write the escrow contract, which would remain as follows:

\begin{haskellcode}
escrow :: Contract
escrow = CommitCash iCC1 1 (ConstMoney 450) 10 100
                    (When (OrObs (two_chose 1 2 3 0)
                                 (two_chose 1 2 3 1))
                          90
                          (Choice (two_chose 1 2 3 1)
                                  (Pay iP1 1 2 (AvailableMoney iCC1) 100
                                       redeem_original)
                                  redeem_original)
                          redeem_original)
                    Null
\end{haskellcode}

The outermost primitive \haskellinline{CommitCash} allows the ``participant 1'' to commit 450 ADA before block 10, 
with the promise that money will be released on block 100 if they are not claimed before that.

The next primitive, \haskellinline{When}, waits for one of three things to happen:
\begin{enumerate}
 \item Two out of three choose $0$.
 \item Two out of three choose $1$.
 \item The block 90 is added to the blockchain.
\end{enumerate}

If the third option happens first, the money is refunded. Otherwise, there is a \haskellinline{Choice} that will 
immediately refund the money to ``participant 1'' unless two out of three chose $1$; in the later case, 
\haskellinline{Pay} will give ``participant 2'' the opportunity to claim the funds available in \haskellinline{iCC1} 
before block 100. If the funds are not claimed before block 100 they will also be refunded to ``participant 1''.

In the next section, we cover the online contract visualisation and interaction tool for Marlowe.
